### 2014-03-07 src/paper.Rnw
update

o <- subset(oprand, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(oprand, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
@

>>>>

oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
@

<<results='asis'>>=
o <- subset(oprand.x, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(oprand.x, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
@

<<results='asis'>>=
o <- subset(oprand.l, kind == 'original')
o.x <- subset(o, select=c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(o.x) <- c('operator', 'r^2', 'm.red', 'm.sd', 'num', 'B*')
print(xtable(o.x, caption='Original', label='table:rando'), include.rownames=FALSE)
# , sanitize.text.function = function(x){x}, include.rownames=FALSE)
@
<<results='asis'>>=
r <- subset(oprand.l, kind == 'randoop')
r.x <- subset(r, select=c('operator','r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier'))
colnames(r.x) <- c('operator', 'r^2', 'm.red','m.sd', 'num', 'B*')
print(xtable(r.x, caption='Randoop', label='table:randr'), include.rownames=FALSE)
@
